---
title: "Visuals - Ecological Network (R) v2"
output: html_notebook
---



```{r}
library('visNetwork')
library('dplyr')
library('tidyverse')
library('Matrix')
library('reshape2')
library('igraph')

Q_table = "..//data//ecopath//edges_Qmatrix_LTL.csv"
stats_table = "..//data//ecopath//nodes_statstab_LTL.csv"

Q_table = "..//data//ecopath//edges_Qmatrix_UTL.csv"
stats_table = "..//data//ecopath//nodes_statstab_UTL.csv"

```


```{r}
mm <- as.matrix(read.table(Q_table, header=T,sep=",", row.names=1))
edges_long <- melt(mm)
edges1 <- rename(edges_long, "from" = "Var1", "to" = "Var2", "weight" = "value")
edges1$to <- gsub('\\.', '-', edges1$to) # matrix converts - to . so convert back

# FILTERS
edges1 <- edges1 %>% filter(weight > 0) # filter zeros out

#det_close_name = "Detritus_Closure" # LTL
det_close_name = "DET_Close" # UTL
edges1 <- edges1 %>% filter(to != det_close_name) 
edges1 <- edges1 %>% filter(from != det_close_name)
nodes1 <- read.table(stats_table, header=T,sep=",", row.names=1)
nodes1 <- nodes1 %>% filter(Name != det_close_name) # filter zeros out


# ARRANGEMENT
# duplicate TL to use as y location
nodes1$y = nodes1$TL

# set plot x location for nodes 
# (if using layout_nicely can't have two nodes w/ same coords!)
#nodes1$x = nodes1$type_x3
nodes1$x = nodes1$type_x2

net <- graph_from_data_frame(d=edges1, vertices=nodes1, directed=T) 


# ////////////////////////////////////////////////////////
# plots
options(repr.plot.width=10, repr.plot.height=20)

# set min size and distortion on box size, just so small groups visible
min_size = 1
size_mult = 2
V(net)$size = sqrt(V(net)$B) * size_mult + min_size
E(net)$width <- sqrt(E(net)$weight) * 0.2
l <- layout_nicely(net)
# layout_with_fr, layout_with_drl, layout_nicely

# https://bookdown.org/hneth/ds4psy/D-3-apx-colors-basics.html
colrs <- c("turquoise", 
           "skyblue",
           "goldenrod1", 
           "maroon3", 
           "lightskyblue1",
           "salmon", 
           "yellowgreen", 
           "tomato", 
           "navajowhite", 
           "lightpink3",
           "aquamarine2", 
           "darkturquoise", 
           "cadetblue",
           "goldenrod2", 
           "plum2", 
           "lightskyblue1",
           "palegreen2", 
           "tan2", 
           "gray90"
           )
V(net)$color <- colrs[V(net)$type_num]

# color based on incoming edges
edge.start <- ends(net, es=E(net), names=F)[,2]
edge.col <- V(net)$color[edge.start]
# ecol <- rep("gray80", ecount(net))
# inc.edges <- incident(net,  V(net)[type=="ZS"], mode="in")
# ecol[inc.edges] <- "plum2"
#inc.edges <- incident(net,  V(net)[type=="NK"], mode="all")
#ecol[inc.edges] <- "darkturquoise"

# the problem with adding axes and labels is with asp (aspect ratio)
# I can't control axis max / min if asp = 1 and if asp = 0 then 
# weird problems arise with edge drawing
plot(net, 
     edge.arrow.size=.5, 
     axes=T,
     #xlim=(c(0,20)), ylim=c(0,20),
     asp=1, rescale=T, 
     vertex.label=V(net)$lbl_shrt,
     vertex.label.font=1,
     vertex.label.cex=0.7,
     vertex.shape="square",
     edge.color=edge.col,
     layout=l)

legend(x=-1.2, y=1.1, c("Nekton","Zoop. Ichthyo.","Zoop. Hard","Zoop. Soft", "Protozooplankton","Phytoplankton","Bacteria", "Detritus"), pch=21,
       col="#777777", pt.bg=colrs, pt.cex=1.4, cex=1, bty="n", ncol=1)

#plot(net, edge.arrow.size=.4, axes=T, asp=0, rescale=F)
#l <- layout_in_circle(net)
#plot(net, edge.arrow.size=.4, edge.curved=.3, layout=l)

# cover the x axis
#rect(-0.2, -3, 11, -1, col = "white", border = "black")
```


```{r}

# res seems to do opposite of expected
png("../figs/network_plot.png", width = 2000, height = 2000, res = 100) # Adjust dimensions/resolution as needed
plot(
  net,
  edge.arrow.size = 0.5,
  vertex.label = V(net)$lbl_shrt,
  vertex.label.font = 10,
  vertex.label.cex = 2,
  vertex.shape = "square",
  edge.color = edge.col,
  layout = l
)
dev.off()

```
```{r}
#det_close_name = "Detritus_Closure" # LTL
hake_1 = "Hake1_0_11" # UTL
hake_2 = "Hake2_juve_12_35"
hake_3 = "Hake3_mat_36_59"
hake_4 = "Hake4_old_60up"
hsl = "Harbour_Seals"
herring_1 = "Herring1_age0"
herring_2 = "Herring2_juve"
herring_3 = "Herring3_mat"
chin_ws_2 = "Chinook2_WS_emar"
chin_ws_3 = "Chinook3_WS_mar"
chin_ws_4 = "Chinook4_WS_spwn"
coho_w_2 = "Coho2_W_emar"
coho_w_3 = "Coho3_W_mar"
coho_w_4 = "Coho4_W_spwn"


edges1 <- edges1 %>% filter(
  to = hake_1 |
  to = hake_2 |
  to = hake_3 |
  to = hake_4 |
  to = hsl |
  to = herring_1 |
  to = herring_2 |
  to = herring_3 |
  to = chin_ws_2 |
  to = chin_ws_3 |
  to = chin_ws_4 |
  to = coho_w_2 |
  to = coho_w_3 |
  to = coho_w_4
    ) 
edges1 <- edges1 %>% filter(
  from = hake_1 |
  from = hake_2 |
  from = hake_3 |
  from = hake_4 |
  from = hsl |
  from = herring_1 |
  from = herring_2 |
  from = herring_3 |
  from = chin_ws_2 |
  from = chin_ws_3 |
  from = chin_ws_4 |
  from = coho_w_2 |
  from = coho_w_3 |
  from = coho_w_4
    ) 
nodes1 <- read.table(stats_table, header=T,sep=",", row.names=1)
nodes1 <- nodes1 %>% filter(
  Name = hake_1 |
  Name = hake_2 |
  Name = hake_3 |
  Name = hake_4 |
  Name = hsl |
  Name = herring_1 |
  Name = herring_2 |
  Name = herring_3 |
  Name = chin_ws_2 |
  Name = chin_ws_3 |
  Name = chin_ws_4 |
  Name = coho_w_2 |
  Name = coho_w_3 |
  Name = coho_w_4
)


```


```{r}
is_igraph(net)
V(net)$y
```




Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
